The Impact of Critical Slicing in SFL\Comment{tatistical Fault Localization}

### 2018-11-10 paper/main.tex
another pass

Spectrum-based fault localization is an approach to pinpointing bugs
in software programs~\cite{FLSurvey2016, DBLP:conf/kbse/JonesH05,
  DBLP:journals/smr/LuciaLJTB14, DBLP:journals/jss/AbreuZGG09}.  In
spectrum-based fault localization, the following is given: a finite
set $\mathcal{C} = \set{c_1,c_2,...,c_M}$ of $M$ system
\emph{components}\footnote{A component can be any source code artifact
  of arbitrary granularity such as a class, a method, a statement, or
  a branch~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; a finite set
$\mathcal{T} = \set{t_1,t_2,...,t_N}$ of $N$ system transactions,
which correspond to records of a system execution, such as test cases;
the error vector $e = \set{e_1,e_2,...,e_N}$, where $e_i = 1$ if
transaction $t_i$ has failed and $e_i = 0$ otherwise; and an $N \times
M$ coverage matrix $\mathcal{A}$, where $\A{ij}$ denotes the
coverage of component $c_j$ in transaction $t_i$.
The pair $(\mathcal{A},e)$ is commonly referred to as
spectrum~\cite{DBLP:journals/stvr/HarroldRSWY00}, and is depicted in~\cite{fig:spectrum-example}.
Several types of spectra exist.
The most commonly used is called hit-spectrum, where the coverage matrix is encoded in terms of
binary \emph{hit} (1) and \emph{not hit} (0) flags, i.e.,
$\A{ij} = 1$ if $c_j$ is involved in $t_i$ and $\A{ij} = 0$
otherwise.

\begin{figure}[h!]
    \centering
    \begin{tabular}{c|cccc|c}
      $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
      $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
      $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
      \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
      $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
    \end{tabular}
    \caption{An example spectrum.}
    \label{fig:spectrum-example}
\end{figure}

The pair $(\mathcal{A},e)$ serves as input to the fault localization technique.
With this input, the next step in this coverage-based technique consists of determining what columns
of the matrix $A$ resemble the error vector $e$ the most.
For that, an intermediate component frequency aggregator is computed:
%
\begin{equation}\label{eq:occurrence}
 n_{pq}(j) = |\{i\mid \A{ij}=p \wedge e_i=q\}|
\end{equation}
%
\noindent where $n_{pq}(j)$ is the number of runs in which the
component $j$ has been active during execution ($p = 1$) or not
($p=0$), and in which the runs failed ($q = 1$) or passed ($q = 0$).
For instance, $n_{11}(j)$ counts the number of times component $j$ has
been involved ($p = 1$) in failing executions ($q = 1$), whereas
$n_{10}(j)$ counts the number of times component $j$ has been involved
in passing executions.

We then calculate similarity to the error vector by means of applying \emph{fault predictors} to
each component to produce a score quantifying how likely it is to be faulty.
Components are then ranked according to such likelihood scores and reported to the user.

>>>>

Spectrum-based fault localization (\sfl) is a statistical fault
localization technique that takes as input a test suite including at
least one failing test and reports on output a ranked list of
components likely to be in fault~\cite{FLSurvey2016,
  DBLP:conf/kbse/JonesH05, DBLP:journals/smr/LuciaLJTB14,
  DBLP:journals/jss/AbreuZGG09}. The following are given in \sfl{}: a
finite set $\mathcal{C} = \set{c_1,c_2,...,c_M}$ of $M$ system
\emph{components}\footnote{A component can be any source code artifact
  of arbitrary granularity such as a class, a method, a statement, or
  a branch~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; a finite set
$\mathcal{T} = \set{t_1,t_2,...,t_N}$ of $N$ system transactions,
which correspond to records of a system execution, such as test cases;
the error vector $e = \set{e_1,e_2,...,e_N}$, where $e_i = 1$ if
transaction $t_i$ has failed and $e_i = 0$ otherwise; and an $N \times
M$ coverage matrix $\mathcal{A}$, where $\A{ij}$ denotes the coverage
of component $c_j$ in transaction $t_i$.  The pair $(\mathcal{A},e)$
is commonly referred to as
spectrum~\cite{DBLP:journals/stvr/HarroldRSWY00}. Figure~\ref{fig:spectrum-example}
shows an example spectrum.
\begin{wrapfigure}[8]{r}{0.29\textwidth}
  \vspace{-2ex}
  \hspace{-3ex}
  \centering
  \small
  \begin{tabular}{c|cccc|c}
    $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
    $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
    $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
    \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
    $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
  \end{tabular}
  \caption{An example spectrum.}
  \label{fig:spectrum-example}
\end{wrapfigure}
Several types of spectra exist.  The most commonly used is called
hit-spectrum, where the coverage matrix is encoded in terms of binary
\emph{hit} (1) and \emph{not hit} (0) flags, \ie{}, $\A{ij} = 1$ if
$t_i$ covers $c_j$ and $\A{ij} = 0$ otherwise.  The pair
$(\mathcal{A},e)$ serves as input to the fault localization technique.
With this input, the next step in this coverage-based technique
consists of determining what columns of the matrix $A$ resemble the
error vector $e$ the most.  For that, an intermediate component
frequency aggregator $n_{pq}(j)$ is computed:
%
\begin{equation}\label{eq:occurrence}
 n_{pq}(j) = |\{i\mid \A{ij}=p \wedge e_i=q\}|
\end{equation}
%
%\noindent
$n_{pq}(j)$ denotes the number of runs in which the
component $j$ has been active during execution ($p = 1$) or not
($p=0$), and in which the runs failed ($q = 1$) or passed ($q = 0$).
For instance, $n_{11}(j)$ counts the number of times component $j$ has
been involved ($p = 1$) in failing executions ($q = 1$), whereas
$n_{10}(j)$ counts the number of times component $j$ has been involved
in passing executions. We then calculate similarity to the error
vector by means of applying \emph{fault predictors} to each component
to produce a score quantifying how likely it is to be faulty.
Components are then ranked according to such likelihood scores and
reported to the user. \Fix{show ochiai here...}

\Mar{----------------------- estou aqui}
